Scoring Patients

### 2016-11-16 Patient Report.Rmd
added markdown file for reporting

cor.scores = as.data.frame(matrix(nrow=length(patient.data$Patient), ncol=2, dimnames=list(patient.data$Patient, c('similar','different'))))
for (patient.name in unique(patient.info$Patient)  )  {
  message(patient.name)
  patient.plot.dir = paste(plot.dir, patient.name, sep='/')

  segvals = read.table(paste(patient.plot.dir, "/",patient.name,"_segmentedCoverage_fitted_gamma",gamma2,".txt",sep=""),sep="\t",stringsAsFactors=F,header=T)
  message( paste(length(which(segvals$n.probes < min.probes)), ' probes below the minimum probe count (',min.probes,')', sep=''))

@@

          sim = sim + signif( sum(rc$r[which(rc$P[,i] < 0.05 & rc$r[,i] > 0),i ])/len, 2)
          diff = diff + signif(sum(rc$r[which(rc$P[,i] < 0.05 & rc$r[,i] < 0),i ])/len,2)
        }  
        cor.scores[patient.name,] = c(sim,diff)

@@

      }
    }
  }
pander(cor.scores, justify='left')

cor.scores$Status = patient.data[which(patient.data$Patient %in% rownames(cor.scores)), 'Status']

@@

`r pander(cor.scores[order(cor.scores$Status, cor.scores$similar),], justify='left', split.tables=F)`

>>>>

cor.scores = as.data.frame(matrix(nrow=length(patient.data$Patient), ncol=3, dimnames=list(patient.data$Patient, c('similar','different','n.probes'))))
for (patient.name in unique(patient.info$Patient)  )  {
  message(patient.name)
  patient.plot.dir = paste(plot.dir, patient.name, sep='/')

  segvals = read.table(paste(patient.plot.dir, "/",patient.name,"_segmentedCoverage_fitted_gamma",gamma2,".txt",sep=""),sep="\t",stringsAsFactors=F,header=T)

  message( paste(length(which(segvals$n.probes < min.probes)), ' probes below the minimum probe count (',min.probes,')', sep=''))

@@

          sim = sim + signif( sum(rc$r[which(rc$P[,i] < 0.05 & rc$r[,i] > 0),i ]), 2)
          diff = diff + signif(sum(rc$r[which(rc$P[,i] < 0.05 & rc$r[,i] < 0),i ]),2)
        }  
        cor.scores[patient.name,] = c(sim,diff,nrow(sample.normalised.segvals))

@@

      }
    }
  }
cor.scores$Status = patient.data[which(patient.data$Patient %in% rownames(cor.scores)), 'Status']

@@

```{r scores, echo=F, message=T, warning=F, fig.height=4,fig.width=4,fig.align='left'} 
pander(cor.scores[order(cor.scores$Status, cor.scores$similar),], justify='left')

ggplot(cor.scores, aes(x=similar,y=different, color=Status)) + geom_point()

ggplot(cor.scores, aes(y=abs(similar+different), x=c(1:nrow(cor.scores)), color=Status)) + geom_point()
